Creating optimal conditions for reproducible data analysis in \R with `fertile'\protect\thanks{The authors gratefully acknowledge contributions from Hadley Wickham, Jenny Bryan, Greg Wilson, Edgar Ruiz, and other members of the \pkg{tidyverse} team.}

### 2020-08-04 STAT-paper-template/APA/fertile.Rnw
added IRB protocol #

To test \pkg{fertile}'s effectiveness, we began an initial randomized control trial of the package on an introductory undergraduate data science course at Smith College in Spring 2020. Unfortunately, however, the trial had to be postponed after the COVID-19 pandemic significantly altered the experimental conditions at the midpoint of testing.

>>>>

To test \pkg{fertile}'s effectiveness, we began an initial randomized control trial of the package on an introductory undergraduate data science course at Smith College in Spring 2020 \footnote{This study was approved by Smith College IRB, Protocol \#19-032}. Unfortunately, however, the trial had to be postponed after the COVID-19 pandemic significantly altered the experimental conditions at the midpoint of testing.
